Untitled

### 2021-01-27 ms/manuscript.Rmd
WIP: tables with kableExtra

>>>>

```{r glmm-table-kableextra, results = "asis"}
group_locs <-
glmm_summary %>% mutate(row_num = 1:nrow(.)) %>% group_by(response) %>%
  summarize(
    start = min(row_num),
    end = max(row_num),
    .groups = "drop"
  )

glmm_summary %>%
  mutate(
    fixed_effects = case_when(
      fixed_effects == "both" ~ "Generation + habit",
      fixed_effects == "intersect" ~ "Generation + habit + Generation:habit",
      TRUE ~ str_to_sentence(fixed_effects)
    ),
    response = str_replace_all(response, "recovery", "Recovery") %>%
      str_replace_all("etr", "ETR~max~") %>%
      str_replace_all("par", "PPFD~95%~"),
    DIC = round_t(DIC, 2),
    delta_DIC = round_t(delta_DIC, 2)
  ) %>%
  select(fixed_effects, response, DIC, delta_DIC) %>%
  kbl(format = "latex", booktabs = TRUE, col.names = c("Fixed effects", "Response", "DIC", "delta DIC")) %>%
  row_spec(which(glmm_summary$delta_DIC == 0), bold = TRUE) %>%
  pack_rows(
    "ETR\\textsubscript{max}", 
    group_locs %>% filter(response == "etr") %>% pull(start),
    group_locs %>% filter(response == "etr") %>% pull(end),
    escape = FALSE)
```
